---
title: "Movies Report"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
source("scripts/audience_rating_chart.r")
source("scripts/bar_graph_budget.r")
source("scripts/gross_vs_budget chart.r")
source("scripts/report_render.r")
source("scripts/summary_information_script.r")
source("scripts/summary_table_code.r")
movies <- read.csv("data/movies.csv")
```

## Introduction

In our dataset, the Movie Industry, we want to better understand the trends of the various characteristics that apply to the external and internal factors of a movie, including the budget, rating, genre, production company, runtime, and so much more. We are analyzing the dataset that spans over three decades: from 1986 - 2016. The purpose of acquiring this dataset is to observe how certain trends have increased, decreased, or stayed the same. An example would be comparing the gross revenue to each genre to analyze which genre generally produces the best selling movies.

#### Summary Information 
  In our Movies dataset, there are `r number_of_cols` columns. The character types for each column are: `r char_types`. There are `r number_of_rows` rows. These are 10 unique values from the movie names column: `r example_movies`.

## Graphs

### Bar Graph

```{r echo=FALSE}
plot(budget_bar_graph(movies))

```

The four charts compares the relationship of how the budget of each type of rating category changes throughout the span of 30 years. Using a bar graph, wrapped into separate rating categories, we are able to see that, besides the rated R category, all the categories increase the budget of the movies throughout the years. We are also able to see that the rated G movie productions have a trend of acquiring a higher budget compared to the other rating categories.

### Line Graph

This chart aims to show and compare the prevalence of different movie ratings over the last 30 years. A line graph emphasizes the rise and falls in the data over time, and ploting the different ratings in different colors on the same graph helps to closely compare their trends. 

```{r audience_rating_vs_time, echo = FALSE}
plot(ratings_chart(movies))
```

#### Important information:
* There has been a rise in PG-13 movies and a decrease in PG movies
* The number of G movies has remained relatively steady with a very low number of films per year
* The R movies tend to be the most frequent but their numbers fluctuate by year.

### Scatter Plot

This is a function that returns a scatter plot by using the given dataframe and comparing to average annual budget to the average annual gross income.

```{r gross_vs_budget chart, echo=FALSE}
plot(budget_vs_income(movies))
```

This chart displays the relationship between the average yearly budget and average yearly gross incomes of movies over a thirty year period. The information was displayed on this type of graph, because it clearly depicts the linear relationship between the variables. Each year, the average budget for movies as well as the average gross income has consistently increased.