---
title: "index.rmd"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
source("scripts/audience_rating_chart.r")
source("scripts/bar_graph_budget.r")
source("scripts/gross_vs_budget chart.r")
source("scripts/report_render.r")
source("scripts/summary_information_script.r")
source("scripts/summary_table_code.r")
movies <- read.csv("data/movies.csv")
```


## Introduction



#### Summary Information 
  In our Movies dataset, there are `r number_of_cols` columns. The character types for each column are: `r char_types`. There are `r number_of_rows` rows. These are 10 unique values from the movie names column: `r example_movies`. 



```{r echo=FALSE}
plot(budget_bar_graph(movies))

```

The four charts compares the relationship of how the budget of each type of rating category changes throughout the span of 30 years. Using a bar graph, wrapped into separate rating categories, we are able to see that, besides the rated R category, all the categories increase the budget of the movies throughout the years. We are also able to see that the rated G movie productions have a trend of acquiring a higher budget compared to the other rating categories.


## Line Graph

This chart aims to show and compare the prevalence of different movie ratings over the last 30 years. A line graph emphasizes the rise and falls in the data over time, and ploting the different ratings in different colors on the same graph helps to closely compare their trends. 

```{r audience_rating_vs_time, echo = FALSE}
plot(ratings_chart(movies))
```

#### Important information:
* There has been a rise in PG-13 movies and a decrease in PG movies
* The number of G movies has remained relatively steady with a very low number of films per year
* The R movies tend to be the most frequent but their numbers fluctuate by year.